The importance of fidelity in the scheduling of Redox Flow Batteries.

### 2018-10-29 Paper/main.tex
Add files via upload

In a techno-economic analysis of this VRFB, use of the LP formulation would therefore lead to errors in calculation of revenue (in this case an overestimation). Use of the NLP formulation to determine scheduling in a practical application would result in significantly higher revenue than would the LP formulation. It would be possible to set a representative voltaic efficiency ($\bar\eta_V$) in the LP formulation such that the estimate of revenue would be closer to that of the NLP formulation, but this value cannot be known \textit{a priori}.

@@

Maximising \cref{eqn: NLP_true_OCV_long_form} subject to \cref{eqn: Cell_Voltage_Constraint} for the 2017 data resulted in \pounds 26.07 compared to \pounds 26.40 when the cell voltage was not constrained. The difference is small because high current-density is already discouraged by the functionalised voltaic losses in \cref{eqn: NLP_true_OCV_long_form}. \cref{fig:V_max_schedules} shows the optimal schedules with and without constraint for 5\textsuperscript{th} February 2017, where the difference in revenue was greatest (\pounds 0.018 vs. \pounds 0.020). \cref{fig:V_max_voltages} shows the corresponding cell-voltage profiles.

\begin{figure}[!ht]
\centering
\subfloat[][]{
\label{fig:V_max_schedules}
\includegraphics[trim = 2cm 8cm 2cm 9cm, clip, width = .5\textwidth]{./V_max_schedules.pdf}
}
\subfloat[][]{
\label{fig:V_max_voltages}
\includegraphics[trim = 2cm 8cm 2cm 9cm, clip, width = .5\textwidth]{./V_max_voltages.pdf}
}
\caption{(a) Optimal VRFB schedules derived for the 5\textsuperscript{th} February 2017 by maximising \cref{eqn: NLP_true_OCV_long_form} with no cell-voltage constraint, and subject to the cell voltage constraint given in \cref{eqn: Cell_Voltage_Constraint}. (b)Corresponding cell-voltage profiles.}
\end{figure}

>>>>

In a techno-economic analysis of this VRFB, use of the LP formulation would therefore lead to meaningful errors in calculation of revenue (in this case an overestimation). Use of the NLP formulation to determine scheduling in a practical application would result in significantly higher revenue than would the LP formulation. It would be possible to set a representative voltaic efficiency ($\bar\eta_V$) in the LP formulation such that the estimate of revenue would be closer to that of the NLP formulation, but this value cannot be known \textit{a priori}.

@@

Maximising \cref{eqn: NLP_true_OCV_long_form} subject to \cref{eqn: Cell_Voltage_Constraint} for the 2017 data resulted in \pounds 26.07 compared to \pounds 26.40 when the cell voltage was not constrained. The difference is small because high current-density is already discouraged by the functionalised voltaic losses in \cref{eqn: NLP_true_OCV_long_form}. \cref{fig:V_max_schedules_no_effect_day} shows the optimal scheduling with and without voltage constraint for the median revenue day 22\textsuperscript{nd} August 2017, and \cref{fig:V_max_voltages_no_effect_day} the corresponding cell voltage profiles, showing a maximum cell-voltage of \SI{1.62}{\volt} and hence no violation in the unconstrained schedule.

\begin{figure}[!ht]
\centering
\subfloat[][]{
\label{fig:V_max_schedules_no_effect_day}
\includegraphics[trim = 2cm 8cm 2cm 9cm, clip, width = .5\textwidth]{./V_max_schedules_no_effect_day.pdf}
}
\subfloat[][]{
\label{fig:V_max_voltages_no_effect_day}
\includegraphics[trim = 2cm 8cm 2cm 9cm, clip, width = .5\textwidth]{./V_max_voltages_no_effect_day.pdf}
}
\caption{(a) Optimal VRFB schedules derived for the 22\textsuperscript{nd} August 2017 by maximising \cref{eqn: NLP_true_OCV_long_form} with no cell-voltage constraint, and subject to the cell voltage constraint given in \cref{eqn: Cell_Voltage_Constraint}. (b) Corresponding cell-voltage profiles.}
\end{figure}

\cref{fig:V_max_schedules} shows the optimal schedules with and without constraint for 5\textsuperscript{th} February 2017, where the difference in revenue was greatest (\pounds 0.018 vs. \pounds 0.020). \cref{fig:V_max_voltages} shows the corresponding cell-voltage profiles.

\begin{figure}[!ht]
\centering
\subfloat[][]{
\label{fig:V_max_schedules}
\includegraphics[trim = 2cm 8cm 2cm 9cm, clip, width = .5\textwidth]{./V_max_schedules.pdf}
}
\subfloat[][]{
\label{fig:V_max_voltages}
\includegraphics[trim = 2cm 8cm 2cm 9cm, clip, width = .5\textwidth]{./V_max_voltages.pdf}
}
\caption{(a) Optimal VRFB schedules derived for the 5\textsuperscript{th} February 2017 by maximising \cref{eqn: NLP_true_OCV_long_form} with no cell-voltage constraint, and subject to the cell voltage constraint given in \cref{eqn: Cell_Voltage_Constraint}. (b) Corresponding cell-voltage profiles.}
\end{figure}
